Measuring matter effects in Neutron star - Black hole binaries with Advanced LIGO

### 2016-04-06 Paper/paper.tex
more changes
first pass at abstract

\begin{abstract}
We attempt to answer the following questions:
\end{abstract}

>>>>

\begin{abstract}
Very recently, the Advanced LIGO (aLIGO) observatories announced the first
terrestrial detection of gravitational waves. This heralds an era of 
observational gravitational wave (GW) astronomy. Neutron star - black hole
(NSBH) binaries are one of the primary sources targeted for observation
with the aLIGO detectors.
% 
GWs from these sources will carry signatures of the tidal distortion of
the NS by the BH during the inspiral, and of its tidal disruption (if that
happens) at merger. In the NS is disrupted, the merger and ringdown signal
is drastically suppressed, which distinguishes it from a BHBH merger.
% 
In this paper, we present a Bayesian study of the measurability of the 
tidal deformability of neutron stars, allowing the companion hole to take 
on a variety of masses and spins.
% 
First, we find that if BHBH templates are used to estimate source 
parameters for an NSBH signal, a significant bias is introduced in the 
inference if the signal-to-noise ratio (SNR) is greater than $\rho=30$.
% 
Second, we find that if we are to get a loud signal with $\rho\geq 23$, 
we can put a factor of two bound on the NS tidal deformability parameter
$\lambdans\propto (R/M)^{5}$.
% 
Finally, we study the improvement in our measurement of $\lambdans$ from 
multiple observations. Using an approximately astrophysical population, 
we find that (i) the median measured $\lambdans$ catches up to within
$10\%$ of the true value in approximately $20$ observations; (ii) the $90\%$
confidence interval for $\lambda$ shrinks to $\pm 50\%$ within the same
number of observatoins.
% 
We find these results encouraging, and recommend that an effort to 
measure $\lambdans$ be taken within the LIGO-Virgo Collaboration once
we begin to detect NSBH coalescences.
\end{abstract}
